Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-23 Paper.tex
Switch transaction order for PoC-4.
Wire protocol tweak.

The function $L_T$ prepares a transaction for being transformed into an RLP-serialised byte array:
\begin{equation}
L_T(T) \equiv \begin{cases}
(T_n, T_v, T_p, T_g, T_t, T_\mathbf{b}, T_\mathbf{i}, T_w, T_r, T_s) & \text{if} \; T_t = 0\\
(T_n, T_v, T_p, T_g, T_t, T_\mathbf{d}, T_w, T_r, T_s) & \text{otherwise} 
\end{cases}
\end{equation}

@@

Specify a block or blocks that the peer should know about. The items in the list (following the first item, 0x13) are blocks as described in the format described in the main specification.
\begin{itemize}
\item $b_0$, $b_1$, ... are the blocks that should be assimilated.
\end{itemize}
}\\
\midrule
0x14 & \textsc{GetChain} & \textsc{Chain} or \textsc{NotInChain} & $(\text{0x}14, p_0 \in \mathbb{B}_{32}, p_1 \in \mathbb{B}_{32}, ..., c \in \mathbb{P})$ \\
& \multicolumn{3}{p{0.8\columnwidth}}{
Request the peer to send $c$ blocks in the current canonical block chain that are children of one of a number of given blocks, according to a preferential order with $p_0$ being the most prefered. If the designated parent is the present block chain head, an empty reply should be sent. If none of the parents are in the current canonical block chain, then a NotInChain message should be sent along with $p_n$, the least preferential parent. If no parents are passed, then a reply need not be made.
\begin{itemize}
\item $p_0$, $p_1$, ... are the SHA3 hashes of the parents of blocks that we should be informed of with a \textsc{Blocks} reply. Typically, these will be specificed in increasing age (or decreasing block number).
\item $c$ is the number of children blocks of the most prefered parent that we should be informed of through the corresponding \textsc{Blocks} reply.
\end{itemize}
}\\
\midrule
0x15 & \textsc{NotInChain} && $(\text{0x}15, p \in \mathbb{B}_{32})$ \\
& \multicolumn{3}{p{0.8\columnwidth}}{Inform the peer that a particular block was not found in its block chain.
\begin{itemize}
\item $p$ is the SHA3 hash of the block that was not found in the block chain. Typically, this will be the least preferential (oldest) block hash given in a previous \textsc{GetChain} message.
\end{itemize}
}\\
\midrule
0x16 & \textsc{GetTransactions} & \textsc{Transactions} & $(\text{0x}16)$ \\
& \multicolumn{3}{p{0.8\columnwidth}}{Request the peer to send all transactions currently in the queue. See \textsc{Transactions}.}\\
\bottomrule
\end{tabular*}

>>>>

The function $L_T$ prepares a transaction for being transformed into an RLP-serialised byte array:
\begin{equation}
L_T(T) \equiv \begin{cases}
(T_n, T_v, T_t, T_p, T_g, T_\mathbf{b}, T_\mathbf{i}, T_w, T_r, T_s) & \text{if} \; T_t = 0\\
(T_n, T_v, T_t, T_p, T_g, T_\mathbf{d}, T_w, T_r, T_s) & \text{otherwise} 
\end{cases}
\end{equation}

@@

Specify a block or blocks that the peer should know about. The items in the list (following the first item, 0x13) are blocks as described in the format described in the main specification.
\begin{itemize}
\item $b_0$, $b_1$, ... are the blocks that should be assimilated.
\end{itemize}
}\\
\midrule
0x14 & \textsc{GetChain} & \textsc{Blocks} or \textsc{NotInChain} & $(\text{0x}14, p_0 \in \mathbb{B}_{32}, p_1 \in \mathbb{B}_{32}, ..., c \in \mathbb{P})$ \\
& \multicolumn{3}{p{0.8\columnwidth}}{
Request the peer to send $c$ blocks in the current canonical block chain that are children of one of a number of given blocks, according to a preferential order with $p_0$ being the most prefered. If the designated parent is the present block chain head, an empty reply should be sent. If none of the parents are in the current canonical block chain, then a NotInChain message should be sent along with $p_n$, the least preferential parent. If no parents are passed, then a reply need not be made.
\begin{itemize}
\item $p_0$, $p_1$, ... are the SHA3 hashes of the parents of blocks that we should be informed of with a \textsc{Blocks} reply. Typically, these will be specificed in increasing age (or decreasing block number).
\item $c$ is the number of children blocks of the most prefered parent that we should be informed of through the corresponding \textsc{Blocks} reply.
\end{itemize}
}\\
\midrule
0x15 & \textsc{NotInChain} && $(\text{0x}15, p \in \mathbb{B}_{32})$ \\
& \multicolumn{3}{p{0.8\columnwidth}}{Inform the peer that a particular block was not found in its block chain.
\begin{itemize}
\item $p$ is the SHA3 hash of the block that was not found in the block chain. Typically, this will be the least preferential (oldest) block hash given in a previous \textsc{GetChain} message.
\end{itemize}
}\\
\midrule
0x16 & \textsc{GetTransactions} & \textsc{Transactions} & $(\text{0x}16)$ \\
& \multicolumn{3}{p{0.8\columnwidth}}{Request the peer to send all transactions currently in the queue. See \textsc{Transactions}.}\\
\bottomrule
\end{tabular*}
